### 2023-10-02 5.Conclusions/further.tex
Pause midi

\subsection{Netlist generator script}

A big upgrade to make would be to have a completly customizable script that works similarly to tensorflow.

>>>>

\subsection{Other \acp{LSTM} variants}

As discused before(\cref{sec:genwei}), they are only two of the \ac{LSTM} variants available in Keras. Nonetheless, it is possible to write custom layer function for Keras. Creating a layer from scratch is very time consuming and not so interresting for the scope the results needed. It can be done to extend the reach of the work.
